workshop

### 2023-03-14 scripts/workshop/workshop.Rmd
fix some errors and knit
host abundances over time

comm_data_2 <- comm_data_1 %>% group_by(WetAltID) %>% filter(!month.n>max_mo)
```

@@

>>>>

comm_data_2 <- comm_data_1 %>% group_by(WetAltID) %>% filter(!month.n>max_mo) %>% ungroup()
```

@@

# Phenology

Let's look at amphibian phenology from the data
 - when do amphibian larvae first appear
 - when are amphibian larvae no longer found (implies emergence)
 - abundance (average clutch size?)

I want each row to be one month in one wetland and have columns for each species abundance
```{r}
ph <- data %>% select(-c(X1, ID, Species, RV.Status, HostDensity, MinWaterTemp, MaxWaterTemp, MeanWaterT, CanopyCover, Stage, SQMean, LogSQMean, ArcSQMean, LogSQMean.1, Date.Collected, SVL, Zscore, Species.4:Species.42, log10_SQ, ln_SQ, log1p_SQ)) %>% filter(Stage2=="L") %>% distinct()
```

condensing this down was more difficult than expected
some things to ask Stacey about
 - some of this might be explained by measurements for one sampling period being taken on separate days
 - discrepancies exist for a single site_month
 - - 19_month4: CanopyCover
 - - 7_month6: HostDensity
 - lots of sites had the same MeanWaterTempPredC but different MeanWaterT
 - - these sites also had different MinWaterTemp and MaxWaterTemp

Also I need to reconsider stage with other analyses. There are about 90 adults. I am just going to filter them out for now and assume the values we have are for larvae only?
 - need to check on this. Do data include adults as well?

Data are now ready. ph only has one of every site-month combo
```{r}
ph_ab <- ph %>% pivot_longer(.,cols = c(AB2:AB42))
ph_ab %>% ggplot(.,aes(x=Month.1, y=value, color=name, group = name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID))
```

```{r}
ph_ra <- ph %>% pivot_longer(.,cols = c(RA2:RA42))
ph_ra %>% ggplot(.,aes(x=Month.1, y=value, color=name, group=name)) + geom_point() + geom_line() + facet_wrap(vars(WetAltID), ncol=1)
```
